Spatial and temporal variability in economic availability of residual biomass from timber harvest in west-central Alberta, Canada (1990--2015)

### 2022-11-18 analysis/ms_november/hrs_2022-11-18_appendix.Rmd
2022-11-18

This appendix adds detail on the creation of some model parameters.

@@

For administrative purposes, the Green Area is divided into Forest
Management Units (FMUs). The province enters into long term agreements
with forest products companies giving the companies the rights to timber
harvest and the responsibility to manage the forest sustainably. These
agreements are called Forest Management Agreements, and the areas under
agreement are called Forest Management Agreement Areas (FMAAs). For the
most part, the boundaries of the FMAAs are coincident with FMU
boundaries, except for the Alberta-Pacific FMAA in eastern Alberta which
comprises 12 FMUs. Maps of the FMUs @AlbertaFMU and the FMAAs @AlbertaFMA can be
found on the Government of Alberta website. The FMU and FMAA boundaries
are used to assign utilization standards (discussed here) and average
piece size (discussed in the next section).

@@

>>>>

This appendix details the calculations used to determine the available forest
residue biomass available on each township in each year of the study period.

@@

For administrative purposes, the Green Area of Alberta is divided into Forest
Management Units (FMUs). The province enters into long term agreements
with forest products companies giving the companies the rights to timber
harvest and the responsibility to manage the forest sustainably. These
agreements are called Forest Management Agreements, and the areas under
agreement are called Forest Management Agreement Areas (FMAAs). For the
most part, the boundaries of the FMAAs are coincident with FMU
boundaries, except for the Alberta-Pacific FMAA in eastern Alberta which
comprises 12 FMUs. Maps of the FMUs @AlbertaFMU and the FMAAs @AlbertaFMA can be
found on the Government of Alberta website. The FMU and FMAA boundaries
are used to assign utilization standards (discussed here) and average
piece size (discussed in the next section).

@@

# References

### 2022-11-18 analysis/ms_november/hrs_2022-11-18_figs.Rmd
2022-11-18

```{r pressure, echo=FALSE, fig.cap="Comparison of actual harvest levels for Alberta from the national forestry database and values estimated for this study."}
knitr::include_graphics("../../img/harv_comparison.png")
#suppressWarnings(print(harv_comparison))

>>>>

<!-- ```{r pressure, echo=FALSE, fig.cap="Comparison of actual harvest levels for Alberta from the national forestry database and values estimated for this study."} -->
<!-- knitr::include_graphics("../../img/harv_comparison.png") -->
<!-- #suppressWarnings(print(harv_comparison)) -->
